Almost compatible functions and infinite length games

### 2015-11-17 articles/almost-compatible-functions-and-topological-games/article.tex
paste in s prime notes

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{game}[theorem]{Game}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}

@@

\section{asdf}

>>>>

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{claim}[theorem]{Claim}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}
      \newtheorem{example}[theorem]{Example}
      \newtheorem{game}[theorem]{Game}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

      \theoremstyle{plain}
      \newtheorem*{theorem*}{Theorem}
      \newtheorem*{lemma*}{Lemma}
      \newtheorem*{corollary*}{Corollary}
      \newtheorem*{proposition*}{Proposition}
      \newtheorem*{conjecture*}{Conjecture}
      \newtheorem*{question*}{Question}
      \newtheorem*{claim*}{Claim}

      \theoremstyle{definition}
      \newtheorem*{definition*}{Definition}
      \newtheorem*{example*}{Example}
      \newtheorem*{game*}{Game}

      \theoremstyle{remark}
      \newtheorem*{remark*}{Remark}

@@

\section{Almost compatible functions}

  \begin{definition}
    \(S'(\theta)\) states that there exists a cofinal family
    \(\mc S\subseteq[\theta]^{\omega}\) and a collection of pairwise
    almost compatible
    finite-to-one functions \(\{f_S\in\omega^S:S\in\mc S\}\)
  \end{definition}

  \begin{definition}
    \(S(\theta)\) strengthens \(S'(\theta)\) by requiring the collection
    to contain one-to-one functions.
  \end{definition}

  We wish to show that Scheeper's original \(S(\theta)\) is strictly stronger
  than \(S'(\theta)\).

  \begin{definition}
    A topological space is said to be \(\omega\)-bounded if each countable
    subset of the space has compact closure.
  \end{definition}

  % TODO: read through Alan's proof and fit to rest of document
          \begin{theorem}
           For each $n\in \omega$, there is a locally countable,
            $\omega$-bounded topology on $\omega_n$. Note
            that this means that the closure of any set has
            the same cardinality and weight as the set.
          \end{theorem}

          To prove the theorem, we must actually prove a stronger lemma.

          \begin{lemma}
          Assume that $X$ has cardinality at most $\omega_n$ (for
          any $n\in \omega$),
          and is locally countable, locally compact, and the closure
          of each set has the same cardinality as the set.
          Then $X$ has an $\omega$-bounded extension with the
          same properties.
          \end{lemma}

            \begin{proof}
            We prove this by induction on $n$.
            In fact, we make our inductive statement that  if $\tilde X$
            is the extension of $X$, then  $\tilde X \setminus X$ also
            has cardinality $\omega_n$.
             If $n=0$,
              then we can just take the free union of two copies of $X$
              and then the one-point compactification.
             So suppose $n>0$ and
            that $X$ is such a topology on the ordinal $\omega_n$.
            For each $\alpha<\omega_n$, the closure of the initial
            segment $\alpha$ is bounded by some $\gamma_\alpha$.
            Also, because $X$ is locally countable, $\gamma_\alpha$
            can be chosen so that $\alpha$ is contained  in the interior
            of $\gamma_\alpha$. There is a cub  $C\subset \omega_n$
            with the property that for each $\delta\in C$ and $\alpha<\delta$,
             $\gamma_\alpha$ is also less than $\delta$. This implies
             that for each $\delta\in C$, the initial segment $\delta$ is
             open, and if $\delta$ has uncountable cofinality, then
              $\delta$ is clopen.

              The proof will be easier to visualize if we now
              identify the points of $X$ with the point set
               $\omega_n\times \{0\}$ and we will add the points
                $\omega_n\times \{1\}$ to create the extension.
             By induction on $\lambda \in C$ we define a topology
             on $\omega_n\times\{0\}\cup \lambda\times \{1\}$ so that
             $\omega_n \times \{0\}$ is an open subset. We also ensure,
             by induction, for each $\alpha<\lambda$,
             the closure of $\alpha\times 2$ is an
              $\omega$-bounded  subset of $\lambda\times 2$.

          In the case that $n=1$, then  choose any sequence
           $\lambda_n : n\in \omega$ increasing cofinal in $\lambda$.
           If $\lambda $ is a limit in $C$, then we simply take the
           topology we have constructed so far on $\lambda\times 2$
           and there's nothing more needs to be done. Otherwise
          we may assume that $\lambda_0$ is the predecessor
          of $\lambda\in C$ and
           we set $Y_\lambda $ to equal the countable set
            $\overline{\lambda}\setminus \lambda$. For convenience,
             and with no loss, we assume that $\lambda$ itself is a limit
             of limits.
           And we have a topology on
           $$\lambda_0\times 2 \cup (\lambda \cup Y_\lambda)\times\{0\}~.$$
            Recursively
            choose clopen sets $U_n$ in this topology
             so that $\lambda_0\times 2\subset U_0$,
             $U_{n}\cup \lambda_{n+1}\times \{0\}$ is contained
              $ U_{n+1}$ while $U_{n+1}$ is disjoint from $Y_\lambda$.
              It is easy to see that we can have all the points
              in $(\lambda\setminus \{\lambda_n : n\in\omega\})\times \{1\}$
              be isolated, and arrange that $(\lambda_n,1) $ is the
              point at infinity in the one-point compactification
              $U_n\cup (\lambda_n\times \{1\})$.

                Now we handle the case $n>1$ and we can shrink $C$
                and now assume
                that $C$ is the closure of $\{\lambda\in C : \mbox{cf}(\lambda)>\omega\}$.
                We again proceed by induction on $\lambda\in C$.  If
                $\lambda$ is a limit in $C$, then there is nothing to do: we
                simply have defined an appropriate topology on
                $\omega_n\times  \{0\}\cup \lambda\times \{1\}$ so that
                for each $\mu\in C\cap \lambda$ with $\mbox{cf}(\mu)>\omega$,
                 $\mu\times 2$ is a clopen $\omega$-bounded subspace.
                In case $\lambda$ is not a limit of $C$, then $\lambda$
                has uncountable cofinality and a predecessor $\mu\in C$.
                We therefore have that $\lambda\times\{0\}$ is clopen
                in $\omega_n\times \{0\}$.
                 We apply the induction hypothesis
                to the space $\lambda\times \{0\} \cup \mu\times 2$ to choose
                the topology on $\lambda\times 2$.

            \end{proof}

  \begin{definition}
    A Kurepa family \(\mc K\subseteq[\theta]^{\omega}\) on \(\theta\)
    satisfies that
    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable
    for each \(A\in[\theta]^\omega\).
  \end{definition}

  \begin{corollary}
    There exists a Kurepa family cofinal in \([\omega_k]^\omega\)
    for each \(k<\omega\).
  \end{corollary}

  \begin{proof}
    This is actually a corollary of an observation of Todorcevic communicated
    by Dow in [TODO cite Gen Prog in Top I]:
    if every Kurepa family of size at most \(\theta\)
    extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
    So the result follows as
    every Kurepa family \(\mc K\) of size \(\omega\) extends to
    the cofinal Kurepa family \([\bigcup\mc K]^\omega\).

    We may alternatively
    obtain the result from the previous topological argument by using the family
    \(\mc K\) of compact sets in the constructed topology on
    \(\omega_k\) as our witness. Of course, every Lindel\"of set in
    a locally countable space is countable. Thus \(\mc K\)
    is cofinal in \([\omega_k]^\omega\)
    since for every countable set \(A\), \(\cl A\) is compact and countable.
    It is Kurepa since for every countable set \(A\), let (TODO)
  \end{proof}

  \begin{theorem}
    \(S'(\theta)\) holds whenever there exists a cofinal Kurepa family on \(\theta\).
  \end{theorem}

  \begin{proof}
    Let \(k<\omega\), and \(\mc K=\{K_\alpha:\alpha<\kappa\}\)
    be a cofinal Kurepa family on \(\theta\).
    We should define \(f_\alpha:K_\alpha\to\omega\) for each \(\alpha<\kappa\).

    Suppose we've defined pairwise almost compatible
    \(\{f_\beta:\beta<\alpha\}\). To define
    \(f_\alpha\), we first recall that \(\mc K\rest K_\alpha\) is countable,
    so we may choose \(\beta_n<\alpha\) for \(n<\omega\) such that
    \(
      \{K_\beta:\beta<\alpha\}\rest K_\alpha \setminus \{\emptyset\}
        =
      \{K_\alpha\cap K_{\beta_n}:n<\omega\}
    \).
    Let \(K_\alpha=\{\delta_{i,j}:i\leq\omega,j<w_i\}\) where
    \(w_i\leq\omega\) for each \(i\leq\omega\),
    \(
      K_\alpha\cap \left(K_{\beta_n}\setminus\bigcup_{m<n}K_{\beta_m}\right)
        =
      \{\delta_{n,j}:j<w_n\}
    \),
    and
    \(
      K_\alpha\setminus\bigcup_{n<\omega}K_{\beta_n}
        =
      \{
        \delta_{\omega,j}:j<w_\omega
      \}
    \).
    Then let \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) for
    \(n<\omega\) and \(f_\alpha(\delta_{\omega,j})=j\) otherwise.

    We should show that \(f_\alpha\) is finite-to-one. Let \(n<\omega\).
    We need only worry about \(\delta_{m,j}\) for \(m\leq n\) since
    \(f_\alpha(\delta_{m,j})\geq m\). Since each
    \(f_{\beta_m}\) is finite-to-one, \(f_{\beta_m}(\delta_{m,j})\leq n\)
    for only finitely many \(j\). Thus \(f_\alpha\) maps to
    \(n\) only finitely often.

    We now want to demonstrate that \(f_\alpha\sim f_{\beta_n}\) for all
    \(n<\omega\). We again need only concern ourselves with \(\delta_{m,j}\) for
    \(m\leq n\) since otherwise \(\delta_{m,j}\not\in K_{\beta_n}\).
    For \(m=n\), we have
    \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) which differs
    from \(f_{\beta_n}(\delta_{n,j})\) for only the finitely many \(j\) which
    are mapped below \(n\) by \(f_{\beta_n}\).
    For \(m<n\) and \(\delta_{m,j}\in K_{\beta_n}\),we have
    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) which can
    only differ
    from \(f_{\beta_n}(\delta_{m,j})\) for only the finitely many \(j\) which
    are mapped below \(m\) by \(f_{\beta_m}\) or the finitely many \(j\)
    for which the
    almost compatible \(f_{\beta_n}\sim f_{\beta_m}\) differ.
  \end{proof}

  \begin{corollary}
    \(S'(\omega_k)\) holds for all \(k<\omega\).
  \end{corollary}

  As noted in [TODO cite Dow],
  Jensen's one-gap two-cardinal theorem under \(V=L\) [TODO cite] can be used
  to show that there exist cofinal Kurepa families on every cardinal.

  \begin{corollary}[\(V=L\)]
    \(S'(\theta)\) holds for all cardinals.
  \end{corollary}

  In particular, \(S(\omega_2)\) fails under \(CH\), showing the two are
  distinct. Actually, \(CH\) is not required to have \(S(\omega_2)\) fail.

  % TODO: read through Alan's proof and fit to rest of document
        We are going to need a technical lemma (available in Kunen).
        \bigskip

        \begin{lemma}
        Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a generic filter,
         and let $\mu\in \omega_2$. Then the final model $V[G]$ can be
         regarded as forcing  with $\operatorname{Fn}(\omega_2\setminus \mu,
         2)$ over the model $V[G_\mu]$.
        In addition, for each $\operatorname{Fn}(\omega_2,2)$-name $\dot A$
        of a subset of $\omega$ (treat as a subset of $\omega\times
        \operatorname{Fn}(\omega_2,2) $),
        there is a canonical name $\dot A(G_\mu)$ where,
        $$\dot A(G_\mu) = \{ (n,p\restriction [\mu,\omega_2))  :
         (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}$$
        and we get that the valuation of $\dot A(G_\mu)$ by the tail
        of the generic, $G_{\omega_2\setminus \mu}$, is the same as
        the valuation of $\dot A$ by the full generic.
        \end{lemma}

        \begin{theorem}
          If we add $\omega_2$ Cohen reals to a model of CH we get
        that Scheepers' $S(\omega_2)$ (still) fails.
        \end{theorem}

        \begin{proof}
        The forcing poset is $\operatorname{Fn}(\omega_2, 2)$.
        Let $\{ \dot f_{A} : A\in [\omega_2]^\omega\}$ be a family of
        names such that $\dot f_{A}$ is a one-to-one function from $A$ into
        $\omega$. It suffices to only consider sets $A$ from the ground
        model.
        \bigskip

        Put all the lemma  stuff in an elementary submodel $M$ of the universe
        (technically of $H(\kappa)$,  or of $V_\kappa$,
         for some large $\kappa$). Standard methods says that we can assume that
         $|M|=\omega_1 =\mathfrak c$ and that $M^\omega\subset M$ (which means
         that every countable subset of $M$ is a member of $M$).
        \bigskip

        Let $\lambda = M\cap \omega_2$ (same as the supremum of $M\cap
        \omega_2$). Consider the name  $\dot f_{[\lambda,\lambda+\omega)}$.
        What is such a name?  We can assume that it is a set of pairs
         of the form $( (\lambda+k,m), p)$ where $p\in \mathop{Fn}(\omega_2,
         2)$ and, of course, $k,m\in \omega$. This is (almost) equivalent to
         saying
         that $p$ forces that $\dot f_{[\lambda,\lambda+\omega)}(\lambda+k) =
         m$. We don't take all such $p$, in fact for each $k,m$ it is enough
        to take a
         countable set of such $p$ to get an equivalent name
         (Kunen calls it a nice name if we take, for each $k,m$ an
        antichain that is maximal among such conditions).
        Given any such name $\dot f$, let $\operatorname{supp}(\dot f)$
        denote the union of the domains of conditions $p$ appearing in the
        name.

         Also let $Y$ equal $\operatorname{supp}(\dot
         f_{[\lambda,\lambda+\omega)})\setminus \lambda$.
         Let $\delta$ denote the order type of
         $Y$ and let the 2-parameter notation
         $\varphi_{\mu,\lambda}$ be the order-preserving function from
        $\mu\cup Y$ onto  the ordinal $\mu+\delta$.  This lifts canonically to
        an order-preserving bijection $\varphi_{\mu,\lambda}:
        \operatorname{Fn}(\mu\cup Y,2) \mapsto
        \operatorname{Fn}(\mu+\delta,2)$.
        Similarly, we make sense of the name
         $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_M$.
        Here simply, for each tuple $(~(k,m)~, p)\in \dot
        f_{[\lambda,\lambda+\omega)}$,
         we have that $(~(k,m)~,\varphi_{\mu,\lambda}(p))$ is in $F_M$.
        Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
        be interpreted in the above sense as giving $F_M$ (which is an element
        of $M$).  Note that we do not regard $\delta$ as fixed here, but
        rather simply depending on the $\operatorname{supp}(\dot
        f_{[\lambda,\lambda+\omega)})$ described above. Other values
        replacing $\lambda>\mu$ will result in their own set $Y$
        and canonical map $\varphi_{\mu,\lambda}$; but one thing we do have to
        assume (or arrange) for other values $\alpha$ replacing $\lambda$
        is that $\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})$
        intersected with
        $\alpha$ is contained in $\mu$.

        Now the object $F_M$ is an
        element of $M$, and $M$ believes this statement is true:
        $$
        (\forall \beta\in\omega_2)~ (\exists \beta<\lambda\in \omega_2)~~~
        \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
        \cap \lambda\subset \mu \ \ \mbox{and}\ \
        F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$$

        But now, this  means that,
        not only is there  an $\alpha\in M$,
        $ F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})$
        but also that there is an increasing sequence
         $\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda$ of
         such $\alpha$'s satisfying that, for each $\xi$
        we have that $\operatorname{supp}(\dot
        f_{[\alpha_\xi,\alpha_\xi+\omega)})$ is contained in $\alpha_{\xi+1}$.

        Choose such a sequence.
         This means that if we let $A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)$ we
         have the name $\dot f_A$ in $M$. This then means that all
         the $( (\beta,m) , p)$ appearing in $\dot f_A$ have the property
         that $\mathop{dom}(p)$ is contained in $M$.
        There is, within $M$, a name $\dot g$ satisfying that
         $\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)$
        for all $k >\dot g(n)$.

        \bigskip

        We now apply the above Lemma using $\mu = \mu_0$ and we are now
        working in the extension $V[G_\mu]$. We will abuse the notation
        and use $\dot f_{[\alpha_n,\alpha_n+\omega)}$ instead of
          $\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})$ as defined in
          the Lemma.
        We work for a contradiction. Something special has now happened,
         namely,  the supports of the names $\{
        \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}$ are pairwise disjoint
        and also disjoint from the support of the name
         $\dot f_{[\lambda,\lambda+\omega)}$ (under the same convention about
         $G_\mu$.  And not only that, these names are pairwise isomorphic (in
         the way that they all map to $F_M$).

        \bigskip

        Since $A$ is disjoint from $[\lambda,\lambda+\omega)$,
        there must be an integer $\ell$
        together with a condition
         $q\in \mathop{Fn}(\omega_2\setminus \mu,2)$ satisfying that for all
         $n>\ell$ , $q$ forces that

        \centerline{
         ``if $k>\dot g(n)$ (since  $\alpha_n+k\in A$) then
         $\dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k) \neq
        \dot f_{[\lambda,\lambda+\omega)}(\lambda +k)$''.}

        Choose $n$ large enough so that $\mathop{dom}(q) \cap [\alpha_n,
        \mu_{n+1})$ is
        empty.
         Choose $q_1<q\restriction \lambda$ (in $M$) so that
        $$ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
         \dot f_{[\alpha_n,\alpha_n+\omega)}) =
        \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
         \dot f_{[\lambda,\lambda+\omega)}) $$
        and then (again in $M$) choose $q_2 < q_1$
        so that it both forces a value
         $L$ on $\ell+\dot g(n)$
        and subsequently forces a value $m$ on
         $\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)$.
        But now, again calculate
        $$ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
        (q_2\restriction \operatorname{supp}(\dot
        f_{[\alpha_n,\alpha_n+\omega)}))$$
        and, by the isomorphisms, we have that $q_3$ forces that
         $\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m$.

        Technically (or with more care)  all of this is taking place in the
        poset $\operatorname{Fn}(\omega_2\setminus \mu,2)$ and this means
        that $q_3$ and $q$ are all compatible with each other.

        Follow
        the bouncing ball: it suffices to consider
         $q(\beta)=e$ and to assume that $q_3(\beta)$ is defined.
        Since $q_3(\beta)$ is defined, we have that
        there is a  $\beta'\in\mathop{dom}(q_2)$ such that $
         \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')$,
        and that $q_3(\beta) = q_2(\beta')$.
        But, by definition of $q_1$, $\beta'\in\mathop{dom}(q_1)$
        and even  that $q_1(\beta') = q(\beta)$.
         Then, since $q_2<q_1$, we have that $q_2(\beta')=q_1(\beta') =
         q(\beta)$. This completes the circle that $q_3(\beta) = q(\beta)$.
        \bigskip

        Finally, our contradiction is that $q_3\cup q_2\cup q$
        forces that
         $k=L+1$ violates the quoted statement above.
        \end{proof}

  On the other hand, it's also consistent that \(S'(\theta)\) can fail.

  \begin{theorem}
    There's a model where \(S'(\omega_\omega)\)
    fails.
  \end{theorem}

  \begin{proof}
          We will need the model constructed in \cite{MR1045371} in
           which an instance of Chang's conjecture
           $(\aleph_{\omega+1},\aleph_\omega) \rlap{$\rightarrow$}\,{\rightarrow}
           (\aleph_1,\aleph_0)$ is shown to fail.

          We can take as a given (as shown in \cite[Theorem 5]{MR1045371}) that we may
          assume that we have a model $V$
          of GCH in which there are regular limit cardinals $\kappa<\lambda$
          satisfying that
          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
          (\kappa^{+\omega+1},\kappa^{+\omega})$.

          What this says is that if $L$ is a countable language
          with at least one unary relation symbol $R$ and
           $M$ is a model of $L$  with base set $\lambda^{+\omega+1}$
          in which the interpretation of $R$ has cardinality
           $\lambda^{+\omega}$, then $M$ has an elementary submodel
           $N$ of cardinality $\kappa^{+\omega+1}$ in which
          $R\cap N$ has cardinality $\kappa^{+\omega}$ (of course
           $R\cap N$ is the interpretation of $R$ in $N$ because
          $N\prec M$).

          The interested reader will want to know that it is shown in
          \cite{MR1045371} that if $\kappa$ is a 2-huge cardinal and $j$ is the 2-huge
          embedding with critical point $\kappa$, then with
           $\lambda = j(\kappa)$ one has that
          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
          (\kappa^{+\omega+1},\kappa^{+\omega})$ holds.
          \bigskip

          Let $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$
          be a scale in $\Pi\{ \lambda^{+n+1} : n\in \omega\}$
           ordered by the usual mod finite coordinatewise
          ordering. For convenience we may assume that $h_\xi(n) \geq
          \lambda^{+n}$ for all $\xi$ and all $n$.  If $P$ is any poset of
          cardinality less than $\lambda^{+\omega}$, then in the forcing
          extension by $P$,  the sequence
          $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$  remains cofinal in
           $\Pi\{ \lambda^{+n+1} : n\in \omega\}$.

          \bigskip

          The forcing notion $\mathbb P_0$ is simply the finite condition
          collapse of $\kappa^{+\omega}$, i.e. $\mathbb P_0 = \left(
           \kappa^{+\omega}\right)^{<\omega}$. In the forcing extension by
           $\mathbb P_0$, one now has that the ordinal $\kappa^{+\omega+1}$
           from $V$ is the first uncountable cardinal $\aleph_1$. Then in this
           forcing extension we let $\mathbb P_1$ be the countable condition
           Levy collapse, $Lv(\lambda,\omega_2)$, which collapses all cardinals
           less than $\lambda$ to have cardinality at most $\aleph_1$. The poset
           $\mathbb P_1$ has cardinality $\lambda$. We treat
          $\mathbb P_1$ as containing $\mathbb P_0$
          as a subposet by identifying each $(p_0,1)$ with $p_0$.
          After forcing with $\mathbb P_0*\mathbb P_1$ we will have
          that $\omega_1$ is the ordinal $\left(\kappa^{+\omega+1}\right)^V$,
           $\omega_2$ is the ordinal $\lambda$, and $\omega_\omega$ is the
           ordinal $\left(\lambda^{+\omega}\right)^V$.

          \bigskip

          Now we assume that we have an assignment $\dot f_{\dot A}$ of a
           $\mathbb P_0*\mathbb P_1$-name of a finite-to-one function from
           $\dot A$ into $\omega$ for each
           $\mathbb P_0*\mathbb P_1$-name of a countable subset of
           $\lambda^{+\omega+1}$. We will obtain a contradiction.

          Let $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$ be an enumeration
          of all the  nice $\mathbb P_0$-names of countable
          subsets of $\lambda^{+\omega}$. For each $\xi\in \lambda^{+\omega+1}$,
           let $\dot f_\xi$ be another notation for $\dot f_{\dot A_\xi}$.
          Since $\mathbb P_0$ forces that $\mathbb P_1$ is countably closed,
          the collection of all nice  $\mathbb P_0$-names will produce all
          the countable sets in the extension by $\mathbb P_0* \mathbb
          P_1$, but $\mathbb P_0*\mathbb P_1$ can introduce new enumerations of
          these names.
          For each $\xi\in \lambda^{+\omega+1}$,
          there is a minimal $\zeta_\xi$ so that $\dot A_{\zeta_\xi}$ is the
          canonical name for the range of $h_\xi$. This means that
           $\dot f_{\zeta_\xi} \circ h_\xi$ is simply the
           $\mathbb P_0 *\mathbb P_1$-name of a finite-to-one function from
           $\omega$ to $\omega$.
            For each $\xi\in \lambda^{+\omega+1}$,
           choose any $p_\xi \in \mathbb P_0*\mathbb P_1$ so that
           there is a nice $\mathbb P_0$-name, $\dot H_\xi$,
           that is forced by
           $p_\xi$  to equal $\dot f_{\zeta_\xi}\circ h_\xi$.
            Choose $\Lambda\subset \lambda^{+\omega+1}$
            of cardinality $\lambda^{+\omega+1}$
            and so that there is a pair $p,\dot H$
            satisfying that $p_\xi = p$ and $\dot H_\xi = \dot H$
            for all $\xi\in \Lambda$. We may assume that $p$
            is in a generic filter $  G$.

          Let $\{ x_\xi : \xi\in \lambda^{+\omega+1}\}$ be any enumeration of
           $H(\lambda^{+\omega+1})$  such that
           $\{ x_\xi : \xi\in \lambda^{+\omega}\}$ is also equal to
           $H(\lambda^{+\omega})$. We choose this enumeration in such a way that
           $x_\xi\in x_\eta$ implies $\xi<\eta$.
          We use relation symbol $R_0$ to code
          (and well order)
           $(H(\lambda^{+\omega+1}), \in)$ as follows: $(\xi,\eta)\in R_0$
          if and only if $x_\xi\in x_\eta$.
          Let $R_1$ be a binary relation on $\kappa^{+\omega}$ so that
          $(\kappa^{+\omega},R_1)$ is isomorphic to $\mathbb P_0$. Let
           $R_2$ be a binary relation on $\lambda$ so that
           $R_2\cap (\kappa^{+\omega}\times \kappa^{+\omega})=R_1$ and
           $(\lambda,R_2)$ is isomorphic to $\mathbb P_0*\mathbb P_1$.
          Let $\psi$ be the poset isomorphism from $\lambda$ to
           $\mathbb P_0*\mathbb P_1$.

          We continue coding. We can code the sequence
           $\{ h_\xi : \xi\in \lambda^{+\omega+1}\}$ as another binary  relation
           $R_3$ on $\lambda^{+\omega+1}$ where $R_3\cap \left(\{\xi\}\times
           \lambda^{+\omega+1}\right) = \{ (\xi,h_\xi(n) ) : n\in \omega\}$
          for each $\xi\in \lambda^{+\omega+1}$. The relation symbol $R_4$ can
          code the sequence $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$
          where $(\xi, \alpha, \zeta) \in R_4$ if and only if
          $(\check \alpha, \psi(\zeta))$ is in the name $\dot A_\xi$.
           Let $R_5$ code this collection, i.e.
           $(\gamma,n,m,\eta)\in R_5$ if and only if
           $(\check{(n,m)}, \psi(\eta))\in \dot H_\gamma$. Also let $R_6$ code
           (equal)  the set $\Lambda$.
          Finally we use the relation symbol $R_7$ to similarly code the
          sequence $\{ \dot f_\xi  : \xi \in \lambda^{+\omega+1}\}$:
           $(\xi, \alpha, n, \zeta) \in R_7$ if and only if
          $(\check {(\alpha,n)}, \psi(\zeta))$ is in the name $\dot f_\xi$.

          Needless to say, the unary relation symbol $R$
          is interpreted as the set $\lambda^{+\omega}$ for the application of
          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
          (\kappa^{+\omega+1},\kappa^{+\omega})$.
           Now  we have defined our model
          $M$  of the language $L= \{\in, R, R_0,\ldots, R_7\}$,
           and we choose an elementary submodel
          $N$ witnessing
          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
          (\kappa^{+\omega+1},\kappa^{+\omega})$. Of course $N$ is really just
          a $\kappa^{+\omega+1}$ sized subset of $\lambda^{+\omega+1}$
          with the additional property that $N\cap \lambda^{+\omega}$ has
          cardinality $\kappa^{+\omega}$.  In the
          forcing extension $N$ has cardinality $\omega_1$ and
           $A= N\cap \lambda^{+\omega}$ is countable.

          We will need the following claim from \cite{MR1045371}

          \begin{claim*} We may assume that $N$ satisfies that
           $N\cap \kappa^{+\omega+1}$ is transitive (i.e. an initial segment).
          \end{claim*}

          \begin{proof}[Proof of Claim]
          Suppose  our originally supplied $N$ fails the conclusion of the
          claim.
          We   know that $\kappa^{+\omega}\in N$,
          (  via $R_1$)
          in which case so is $\kappa^{+\omega+1}$.

          Then set $\beta_0 = \sup(N\cap \kappa^{+\omega+1})$ and consider the
          Skolem closure $\mathop{Hull}(N\cup \beta_0, M)$.  A little informally
          (in that we have to formalize the enumeration of formulas)
          let $\{\varphi_n : n\in \omega\}$ is the enumeration of all formulas
          in the language $L$, and let  $\ell_n$ be the minimal integer such
          that the free variables of $\varphi_n$ are among
           $\{ v_0, \ldots, v_{\ell_n}\}$.
          Then,   for each tuple
          $\langle \xi_1,\ldots, \xi_{\ell_n} \rangle$
          of elements of $\lambda^{+\omega+1}$,
           we define $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be
           the minimal $\xi_0\in \lambda^{+\omega+1}$ such that
           $M\models \varphi_n(\xi_0,\ldots, \xi_{\ell_n})$.
          If there is no such $\xi_0$,
             in other words if $M\models \lnot\exists x~~  \varphi_n(x,\xi_1,
          \ldots,\xi_{\ell_n})$, then set
           $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be $0$.
          Now $\mathop{Hull}(N\cup \beta_0,M)$ is just the minimal superset
           $X$
          of $N\cup \beta_0$ that satisfies that
           $f_n[X^{\{1,\ldots,\ell_n\}}] \subset X$ for all $n$. Since this is
           simply a large algebra, we can generate all the terms $t$ of
          the algebraic operations $\{ f_n : n\in \omega\}$.
          It is easily seen that for each $\zeta \in X$, there is a term
          $t(v_1,\ldots, v_m)$ such that $\zeta  = t(\delta_1,\ldots, \delta_m)$
           for some sequence $\langle \delta_1,\ldots, \delta_m\rangle$ with
           each $\delta_i\in  N\cup \beta_0$.
           Assume that
            $\zeta\in \kappa^{+\omega+1}$. By
            re-indexing the variables in the term we can assume
            that there is an $n\leq m$ so that
             $\delta_i  <\beta_0$ for $1\leq i\leq n$
              and $\kappa^{+\omega+1}\leq \delta_i$ for $n<i\leq m$.
              Let $\vec a $ denote
              the tuple $\langle \delta_{n+1},\ldots, \delta_m\rangle$.
            Choose $\eta\in N\cap \kappa^{+\omega+1}$ large enough so that
           $ \{  \delta_1, \ldots, \delta_n\}$ is contained in  $\eta$. Since set-membership
           in $M$ is coded by $R_0$ rather than $\in$ we have to argue a little
           less naturally.
           Consider the set
             $s_0(\eta,\vec a) = \{ t(\gamma_1,\ldots, \gamma_n,\vec a) :
          \{\gamma_1,\cdots,\gamma_n\} \in [\eta]^{\leq n}\}$. Clearly
           $s_0(\eta,\vec a)$ is a member of $H(\lambda^{+\omega+1})$.
           Now define $s_1(\eta,\vec a) $ to be
           $\{ x_\alpha : \alpha\in s_0(\eta, \vec a)\}$,
           and choose the
           unique $\zeta_1\in \lambda^{+\omega+1}$ such
           that $x_{\zeta_1} = s_1(\eta,\vec a)$. We claim that $\zeta_1\in N$.
           Note that $\alpha R_0\zeta_1$ holds if and only if
            $ \alpha \in s_0(\eta,\vec a)$, and therefore
           $$M\models (\forall \alpha)\left[\alpha R_0 \zeta_1 ~~\mbox{iff}~~
           (\exists   \gamma_1\in \eta)\cdots(\exists \gamma_n\in\eta)(\alpha=
           t(\gamma_1,\ldots, \gamma_n,\vec a))\right]~.$$
           By elementarity then we have that $\zeta_1\in N$,
           and by similar reasoning the supremum, $\zeta_0$,
          of $\zeta_1\cap \kappa^{+\omega+1}$ is also in $N$.
             This of course means that $\zeta < \xi_0$.
          \end{proof}

          We use the elementarity of
           $N$  to deduce properties of the families
           $\{ \dot A_\xi : \xi\in N\}$ and $\{ \dot f_\xi : \xi \in
           N\}$.  Actually the collection we are most interested in
           is the family $\{ h_\xi : \xi\in \Lambda\cap N\}$.
